Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
fixed couple technical errors, added comments inline in related work section

We compared the 10 most concerning scenarios when sharing with an app's servers versus with a human audience (friends, work contacts, and the public). We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same:

\begin{packed_enum}
\item Bank account information
\item A video of you unclothed
\item Social security number
\item Video of you entering your PIN
\item An incriminating/embarrassing photo of you
\item A photo of you unclothed
\end{packed_enum}

@@

\subsection{Limitations}
One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearables and their capabilities. 83\% of our participants reported that they do not own a wearable device, but at this time, about ~15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo. We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearable device owners or people specifically interested in wearables. However, that will also have its own bias and limitations as well, since they would not reflect the general population. We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.

@@

\subsection{Ubiquitous Sensing}
Due to new technological advances, we are rapidly moving towards ubiquitous sensing and data capture~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices. Many have worked to discover how privacy will be preserved in world of nearing omni-present sensors. Examples of such efforts include frameworks to design for privacy environments~\cite{bellotti1993design} and evaluating ubiquitous computing applications~\cite{scholtz2004toward}. There are also various models for understanding privacy with respect to ubiquitous computing, including a risk-based model~\cite{hong2004privacy} and a social-based model~\cite{jiang2002approximate}.

@@

\subsection{Smartphones and Wearables Concerns}
Only efforts to improve end-user security which are grounded in user research directly address end-user concerns.The current state of smartphone security and privacy can be attributed to studies conducted to understand user attitudes toward security and privacy for smartphones~\cite{chin2012measuring}, observe behaviors of new smartphone users~\cite{palen2000going}, investigate user understanding of permissions~\cite{felt2012android}.

@@

\subsection{User Perceptions and Behaviors}
While user perceptions are insightful, it has been shown that people generally lack enough information to make privacy-sensitive decisions; even if they do, they are likely to trade off long-term privacy for short-term benefits ~\cite{acquisti2005privacy}. Actual behavior deviates from self-reported behaviors ~\cite{jensen2005privacy} and privacy preferences ~\cite{spiekermann2001privacy}.

>>>>

We compared the 10 most concerning scenarios when sharing with an app's servers versus with a human audience (friends, work contacts, and the public). We observed that there was a substantial overlap between these groups, in that 6 of the most concerning scenarios were the same: \\[-.8cm]

\begin{packed_enum}
\item Bank account information
\item A video of you unclothed
\item Social security number
\item Video of you entering your PIN
\item An incriminating/embarrassing photo of you
\item A photo of you unclothed \\[-.8cm]
\end{packed_enum}

@@

\subsection{Limitations}
One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearables and their capabilities. 83\% of our participants reported that they do not own a wearable device, but at this time, about 15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo. We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearable device owners or people specifically interested in wearables. However, that will also have its own bias and limitations as well, since they would not reflect the general population. We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.

@@

\subsection{Ubiquitous Sensing}
{\color{red} this section is still rough! David will redo.} 
Due to new technological advances, we are rapidly moving towards ubiquitous sensing and data capture~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices. Many have worked to discover how privacy will be preserved in world of nearing omni-present sensors. Examples of such efforts include frameworks to design for privacy environments~\cite{bellotti1993design} and evaluating ubiquitous computing applications~\cite{scholtz2004toward}. There are also various models for understanding privacy with respect to ubiquitous computing, including a risk-based model~\cite{hong2004privacy} and a social-based model~\cite{jiang2002approximate}.

@@

\subsection{Smartphones and Wearables Concerns}
{\color{red} this section is still rough! David will redo.} 
Only efforts to improve end-user security which are grounded in user research directly address end-user concerns.The current state of smartphone security and privacy can be attributed to studies conducted to understand user attitudes toward security and privacy for smartphones~\cite{chin2012measuring}, observe behaviors of new smartphone users~\cite{palen2000going}, investigate user understanding of permissions~\cite{felt2012android}.

@@

\subsection{User Perceptions and Behaviors}
{\color{red} this section is still rough! David will redo.} 
While user perceptions are insightful, it has been shown that people generally lack enough information to make privacy-sensitive decisions; even if they do, they are likely to trade off long-term privacy for short-term benefits ~\cite{acquisti2005privacy}. Actual behavior deviates from self-reported behaviors ~\cite{jensen2005privacy} and privacy preferences ~\cite{spiekermann2001privacy}.
